### 2013-04-20 inst/examples/BUGS/2013-04-19-bayesian-parametric-uncertainty-sdp.Rmd
without uncertainty invariance parameters

@@

```{r}
knit("allen.Rmd")

pardist <- mcmcall
#pardist[,1] = p[2] + rnorm(100, 0, 0.000001)
#pardist[,4] = p[1] + rnorm(100, 0, 0.000001)
#pardist[,5] = p[3] + rnorm(100, 0, 0.000001)

sdp = f_transition_matrix(f, p, x_grid, h_grid, sigma_g, pardist)
s_opt <- value_iteration(sdp, x_grid, h_grid, OptTime=1000, xT, profit, delta)
#opt <- find_dp_optim(sdp, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)

SDP_Mat <- determine_SDP_matrix(f, p, x_grid, h_grid, sigma_g)
pars_fixed <- value_iteration(SDP_Mat, x_grid, h_grid, OptTime=1000, xT, profit, delta)

require(reshape2)
policies <- melt(data.frame(stock=x_grid, pars.uncert = x_grid[s_opt$D], pars.fixed = x_grid[pars_fixed$D]), id="stock")

ggplot(policies, aes(stock, value, color=variable)) + geom_point(alpha=.5) + xlab("stock size") + ylab("harvest")

ggplot(policies, aes(stock, stock - value, color=variable)) + geom_line(alpha=1) + xlab("stock size") + ylab("escapement") 
```

>>>>

---
layout: post
category: ecology
tags:
- nonparametric-bayes

---

Adapting the parametric uncertainty represented by the posterior distributions of the Bayesian estimate (see [earlier notes](http://carlboettiger.info/2013/04/12/parametric-bayesian-example.html)) to the stochastic dynamic programming solution for the optimal policy.  Simply requires evaluating the expectation over the distribution, but is computationally intensive given the spread and the three parameters.

@@

Run the Bayesian analysis to obtain posterior distributions for parameters.

```{r, echo=TRUE, include=FALSE}
knit("allen.Rmd")
```

## Test case using perturbed parameters

First, sanity test. Use the correct parameter values (slightly perturbed).

```{r}
pardist <- mcmcall
pardist[,1] = p[2] + rnorm(100, 0, 0.000001)
pardist[,4] = p[1] + rnorm(100, 0, 0.000001)
pardist[,5] = p[3] + rnorm(100, 0, 0.000001)
```

Compute optimal policy

```{r}
sdp = f_transition_matrix(f, p, x_grid, h_grid, sigma_g, pardist)
s_opt <- value_iteration(sdp, x_grid, h_grid, OptTime=1000, xT, profit, delta)
```

Compare to the case without parameter uncertainty (growth noise only)

```{r}
SDP_Mat <- determine_SDP_matrix(f, p, x_grid, h_grid, sigma_g)
pars_fixed <- value_iteration(SDP_Mat, x_grid, h_grid, OptTime=1000, xT, profit, delta)
```

Plot results

```{r}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, pars.uncert = x_grid[s_opt$D], pars.fixed = x_grid[pars_fixed$D]), id="stock")
ggplot(policies, aes(stock, stock - value, color=variable)) + geom_line(alpha=1) + xlab("stock size") + ylab("escapement") 
```

## Using actual estimates

```{r}
pardist <- mcmcall
```

Transform parameters back

```{r}
pardist[,4] = exp(pardist[,4])
pardist[,5] = exp(pardist[,5])
```

Compute optimal policy

```{r}
sdp = f_transition_matrix(f, p, x_grid, h_grid, sigma_g, pardist)
s_opt <- value_iteration(sdp, x_grid, h_grid, OptTime=1000, xT, profit, delta)
```

Compare to the case without parameter uncertainty (growth noise only)

```{r}
SDP_Mat <- determine_SDP_matrix(f, p, x_grid, h_grid, sigma_g)
pars_fixed <- value_iteration(SDP_Mat, x_grid, h_grid, OptTime=1000, xT, profit, delta)
```

Plot results

```{r}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, pars.uncert = x_grid[s_opt$D], pars.fixed = x_grid[pars_fixed$D]), id="stock")
ggplot(policies, aes(stock, stock - value, color=variable)) + geom_line(alpha=1) + xlab("stock size") + ylab("escapement") 
```

## To Do

So far this is just a proof of principle example.

* Needs to be adjusted to account for uncertainty in the estimates of the noise processes as well. 
* Needs to be written as generic and documented functions, add to nonparametric-bayes package routines.

### 2013-04-20 inst/examples/BUGS/allen.Rmd
without uncertainty invariance parameters

```{r}
mcmc <- as.mcmc(jagsfit)
mcmcall <- mcmc[,-2]
who <- colnames(mcmcall)
mcmcall <- cbind(mcmcall[,1],mcmcall[,2],mcmcall[,3],mcmcall[,4],mcmcall[,5])
colnames(mcmcall) <- who
```

>>>>

```{r}
mcmc <- as.mcmc(jagsfit)
mcmcall <- mcmc[,-2]
who <- colnames(mcmcall)
who 
mcmcall <- cbind(mcmcall[,1],mcmcall[,2],mcmcall[,3],mcmcall[,4],mcmcall[,5])
colnames(mcmcall) <- who
```
